\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2015-01-27 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
added more details about PML to the manual (about regular elements inside the PMLs for better time stability)

>>>>

If you use PML and an external mesh (created using an external meshing tool 
such as CUBIT/TRELIS or similar), try to have elements inside the PML as regular as possible, 
i.e. ideally non-deformed cubes obtained by `extrusion' of regular surface mesh elements meshing the
outer edges of the computational domain without PML; by doing so, the PMLs obtained will be far more stable
in time (PML being weakly unstable from a mathematical point of view, very deformed mesh elements
inside the PMLs can trigger instabilities much more quickly).
